### 2019-03-29 thesis-template/msc-thesis.tex
update

% Add a brief summary of your topic and contributions (Zusammenfassung) in German *and* in English:
\chapter*{Zusammenfassung}
\input{zusammenfassung}
\newpage

@@

As a basis, we derive a simple light propagation scheme for Cartesian grids, which satisfies propagation attenuation and energy-conservation principles and is able to approximate light distributions for given light source position(s) and direction(s) until convergence. The transmission profiles within this grid are considered as crystal fiber structures as an underlying physical model. The consequent task is to model anisotropic fibre structures with the orientation and anisotropy ratios of the underlying tensor field in the grid.
For this, we create an eigenframe by PCA (principal component analysis) for every cell of the tensor field and form an ellipsoid equation as transmission (transfer) function for the transmitted light profiles. We measure impulse responses of the tensor field with Delta-Pulses as light sources at any (sampled) position and direction to generate a uniform sampled map of the global illumination distributions. This map is considered as a global illumination energy flow field.
We gain inspiration by vector field particle tracing's FTLE approach for analyzing the gradient of the flow field of the resulting light distributions. Similar to how the FTLE detects ridges/LCS (Lagrangian Coherent Structures) in vector fields (flow fields), our approach detects these structures, attracting/repelling/saddling tensor field lines (TFL) which frequently represent key structures in nature, in tensor fields. Note that the resulting scalar field is $(n+1)$-dimensional ($x,y,z$ and direction $\theta$) and needs to be flattened by averaging or projection in 3D for proper visualization. We denote this entity a global illumination gradient which states an alternative FTLE-related approach for visualizing LCS in tensor fields through analysis of the directed light transport. 
We also introduce Deformation Ellipsoid Glyphs which are, additionally to visualizing anisotropic topology, pointing inward/outward for compressive/tensile stresses visualizing orientation of mechanical stresses.
We evaluate our approaches for plausibility and comparability within an extensive test campaign.
\newpage

>>>>

% Add a brief summary of your topic and contributions (Zusammenfassung) in German *and* in English:
\chapter*{Zusammenfassung}
%\input{zusammenfassung}

Mithilfe von globalen Beleuchtungsmodellen/-techniken entwickeln wir eine neue Methode um Tensorfelder zu visualisieren, die meistens in Verbindung mit mechanischen Spanunngsverteilungen in 2D/3D-Gittern gebracht werden (vgl. Cauchy-Stress Tensor) , die aber auch andere praktische Bedeutungen in der Physik haben. Als Grundlage leiten wir ein einfaches Lichtausbreitungsschema für kartesische Gitter ab, dass die Prinzipien der Ausbreitungsdämpfung und Energieerhaltung beachtet und Lichtverteilung/en für gegebene Lichtquellenrichtung/en und -positionen bis zur Konvergenz approximieren kann. Als unterliegendes Modell werden die Transmissionsprofile innerhalb diesem Gitter als Kristallfiberstruktur angenommen (vgl. Edelsteine: Katzenaugeneffekt beim Tigerauge). Die folgende Aufgabe ist es, anisotrope Fiberstrukturen mit der Orientierung und den Anisotropiemaßen des unterliegenden Tensorfelds zu modellieren. Dafür erstellen wir per Hauptachsentransformation (PCA) ein Eigensystem für jede Zelle des Tensorfelds und modellieren eine zugehörige Ellipsengleichung als (Transfer-/Wichtungs-) Transmissionsprofil. Wir messen Impulsantworten des Tensorfelds mit Delta-Pulsen an jeder Position und in jede Richtung um eine uniform gesamplete Map der globalen Lichtverteilungen zu erhalten. Diese Map wird als ein globales Energieflussfeld betrachtet. Wir lassen uns von der Technik FTLE aus dem Bereich Particle Tracing der Vector Field Visualization inspirieren, indem wir den Gradient des Flussfelds der resultierenden Lichtverteilungen analysieren und visualisieren. Ähnlich wie FTLE in Vektorfeldern Gräte/Kämme/LCS detektiert, erfasst unsere Methode dieselben Strukturen, anziehende/abstoßende/sattelnde Tensorfeldlinien die häufig Schlüsselstrukturen in der Natur repräsentieren, in Tensorfeldern.Man beachte, dass das resultierende berechnete Skalarfeld (Betrag des Gradienten) $(n+1)$-dimensional ($x,y,z$ und Richtung $\theta$) ist und in 3D für sinnvolle Visualisierung durch Mittelung/Projektion eine Dimension abgeflacht werden muss. Wir führen diese Größe als Global Illumination Gradient ein, der einen FTLE-verwandten Ansatz darstellt, um LCS in Tensorfeldern durch die Analyse des globalen, durch einen Imprint (Gravur in kristallinen Fiberstrukturen) gerichteten Lichtflusses, zu visualisieren. Außerdem führen wir Deformation Ellpsoid Glyphen ein, die zusätzlich zur Darstellung der anisotropen Topologie die Richtung(Zug-/Druck) der Spannung durch Pfeile nach innen/außen darstellen.
\newpage

@@

As a basis, we derive a simple light propagation scheme for Cartesian grids, which satisfies propagation attenuation and energy-conservation principles and is able to approximate light distributions for given light source position(s) and direction(s) until convergence. The transmission profiles within this grid are considered as crystal fiber structures as an underlying physical model (eg. gemstones: tiger's eye's cat's eye effect). The consequent task is to model anisotropic fibre structures with the orientation and anisotropy measures of the underlying tensor field in the grid.
For this, we create an eigenframe by PCA (principal component analysis) for every cell of the tensor field and form an ellipsoid equation as transmission (transfer/weighting) function for the transmitted light profiles. We measure impulse responses of the tensor field with Delta-Pulses as light sources at any (sampled) position and in any direction to generate a uniform sampled map of the global illumination distributions. This map is considered as a global illumination energy flow field.
We gain inspiration by vector field particle tracing's FTLE approach for analyzing the gradient of the flow field of the resulting light distributions. Similar to how the FTLE detects ridges/LCS (Lagrangian Coherent Structures) in vector fields (flow fields), our approach captures these structures likewise, attracting/repelling/saddling tensor field lines (TFL) which frequently represent key structures in nature, in tensor fields. Note that the resulting scalar field is $(n+1)$-dimensional ($x,y,z$ and direction $\theta$) and needs to be flattened by averaging or projection in 3D for proper visualization. We denote this entity a global illumination gradient which states an FTLE-related approach for visualizing LCS in tensor fields through analysis of the global and light transport  directed by imprint/engraving in crystelline fiber structures. 
We also introduce Deformation Ellipsoid Glyphs which are, additionally to visualizing anisotropic topology, pointing inward/outward for compressive/tensile stresses visualizing orientation of mechanical stresses.
We evaluate our approaches for plausibility and comparability within an extensive test campaign.
\newpage
